Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-03-23 paper/paper.tex
20200323 14:41

\section{\label{sec:SectionI}Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems. In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interests in condensed matter physics. For nearest-neighbor (NN) spin-1/2 antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order \cite{PhysRevB.42.4800,PhysRevB.46.11137}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy. The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. As pointed out by Jackeli and Khaliullin \cite{Khaliullin2005, PhysRevLett.102.017205}, the elementary ingredients for realizing this highly anisotropic spin model are strong relativistic spin-orbit coupling (SOC), electron interactions, and specific geometric structure: edge sharing octahedra with 90$^\circ$ TM-O-TM bond angles. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model. It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevLett.118.107203,PhysRevLett.118.107203,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}$=1/2 moments. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

On the experimental side, the discovery of YbMgGaO$_4$ has invoked increasing interest in searching for rare-earth based spin-frustrated materials \cite{srep16419,PhysRevLett.115.167203,PhysRevB.94.035107,PhysRevB.96.054445,PhysRevB.97.184413,PhysRevB.97.125105,PhysRevB.96.075105,PhysRevLett.119.157201}. The Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra \cite{srep16419,PhysRevLett.115.167203}. Extensive studies of magnetic properties using neutron scattering \cite{Nature20614,nphys3971,PhysRevLett.117.267202,PhysRevX.8.031001}, muon spin relaxation ($\mu$SR) \cite{PhysRevLett.117.097201}, electron spin resonance (ESR) \cite{PhysRevLett.115.167203} reveal a possible gapless quantum spin liquid (QSL) ground state. More recently, a class of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,arXiv1911.12712}. The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.

@@

The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization methods are introduced in Sec.~\ref{sec:SectionII}. Section~\ref{sec:SectionIII} discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states. The global phase diagram of the quantum model is presented in Sec.~\ref{sec:SectionIV} along with a discussion of its phases. In Sec.~\ref{sec:SectionV}, we study the moment direction of the quantum FM and stripe states, which provide characteristics to distinguish these phases.

@@

\subsection{\label{sec:SectionIIB}Exact Diagonalization}
We perform a Lanczos ED calculation of the GS energy of the Hamiltonian~\eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC). To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics. Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified. The remaining phases were identified mainly by examining the static magnetic structure factor (SMSF)
\begin{equation}
    S(\bm{Q}) = \frac{1}{N} \sum_{ij} e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \langle \bm{S}_i \bm{\cdot} \bm{S}_j \rangle \label{eq:SMSF}
\end{equation}
where N is the total number of spins, $\bm{R}_i$ is the position of site $i$ and $\langle \bm{S}_i \bm{\cdot} \bm{S}_j \rangle$ is the average over the ground state.

To extract the moment direction of a magnetic ordered phase from a cluster ground state, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions. The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$
\begin{equation}
    | \Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle \label{eq:ClusterCoherentState}
\end{equation}
where the spin-1/2 coherent state
\begin{equation}
    | \theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle \label{eq:Spin-1/2CoherentState}
\end{equation}
is fully polaried along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$. By calculating the overlap with the exact cluster GS, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.

@@

For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane. An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction. When $\Gamma=0, K<0$, the moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\mathbf{S}_1$ direction. All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation. However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$.

@@

In this section, we turn to study the quantum phases in the $J-K-\Gamma$ model Hamiltonian. We consider a $4 \times 6$ cluster with PBC that has been used previously to study the HK model on triangular lattice \cite{KaiLi2015}. The resulting phase diagrams for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:PhaseDiagram}(a). The phase boundaries are obtained from the location of singular features in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$. The quantum phase diagram is closely resemble to the classical result in Ref~\onlinecite{PhysRevB.92.165108} except for the small green area near $\Gamma=1$ which does not appear in the classical phase diagram.

In the HK limit, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified in addition to the well-understood FM ($J=-1$)and 120$^\circ$ N\'{e}el ($J=1$) phases. Under the transformation, we obtain a collinear stripe order (see Fig.~\ref{fig:PhaseDiagram}(b)-(d)) from the original FM order and a noncollinear spiral order (dual N\'{e}el) from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)). The phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.

@@

When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid. To identify the remaining phases and providing more information of these phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}. For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order. Take into account of the classical results, we propose the three blue areas with different shadings in the global phase diagram (see Fig.~\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the Sec.~\ref{sec:SectionV}. In Fig.~\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit. It is worth to note that even the GS of the classical model near the AF Kitaev point was identified to be nematic ordered which is energetically degenerate with the stripe state, our ED results favor the idea that quantum flucations would select a stripe state. The four stripe phases designated as Stripe-A, Stripe-B, Stripe-C, Stripe-D in Fig.~\ref{fig:PhaseDiagram}(a) different from each other only in the moment direction. Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:PhaseDiagram}(a). For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ and Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase. \textcolor{red}{$\cdots \cdots$}

@@

\subsection{\label{sec:SectionVA}Moment direction of the FM phases}
For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction(i.e., $x$, $y$, $z$ direction). However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction. To extract the moment direction of the FM-A and FM-C phases, we construct the following cluster spin-coherent state
\begin{equation}
    |\Psi(\theta, \phi) \rangle = \bigotimes_{i=1}^N|\theta,\phi \rangle
\end{equation}
and calculate the probabilities $P(\theta, \phi)$ with varying $\theta$ and $\phi$. The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b). For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane with all directions degenerate, as expected from classical considerations (see the green dashed line). As for the FM-C phase, the probability is clearly peaked at the direction perpendicular to the lattice plane which is also consistent with our classical analysis (marked by the green solid circle).

>>>>

\section{\label{sec:SectionI}Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems. In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interests in condensed matter physics. For nearest-neighbor (NN) spin-1/2 antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a spin liquid state \cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy. The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. Khaliullin \emph{et al.,} \cite{Khaliullin2005, PhysRevLett.102.017205} proposed to realized this highly anisotropic spin model in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates $A_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. The resulting Hamiltonian is the Kitaev-Heisenberg (KH) model. It was later extended to contains more terms such as the off-diagonal $\Gamma$ term \cite{PhysRevLett.112.077204}. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the KH model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

On the experimental side, the discovery of YbMgGaO$_4$ has invoked increasing interest in searching for rare-earth based spin-frustrated materials \cite{srep16419,PhysRevLett.115.167203,PhysRevB.94.035107,PhysRevB.96.054445,PhysRevB.97.184413,PhysRevB.97.125105,PhysRevB.96.075105,PhysRevLett.119.157201}. The Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra \cite{srep16419,PhysRevLett.115.167203}. More recently, a class of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,arXiv1911.12712}. The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.

@@

The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization (ED) methods are introduced in Sec.~\ref{sec:SectionII}. Section~\ref{sec:SectionIII} discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states. The global phase diagram of the quantum model is presented in Sec.~\ref{sec:SectionIV} along with a discussion of its phases. In Sec.~\ref{sec:SectionV}, we study the moment direction of the quantum FM and stripe states, which provide characteristics to distinguish these phases.

@@

\subsection{\label{sec:SectionIIB}Exact Diagonalization}
We perform Lanczos ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC). To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics. Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified. The remaining phases were identified mainly by examining the static magnetic structure factor (SMSF) $S(\bm{Q})$ and dynamic spin excitation spectrum $A(\bm{k}, \omega)$
\begin{subequations}
    \begin{align}
        & S(\bm{Q}) = \frac{1}{N} \sum_{ij} \langle \Omega | \bm{S}_i \bm{\cdot} \bm{S}_j | \Omega \rangle e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \label{eq:SMSF} \\
        & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} G(\bm{k}, \omega) \label{eq:Akomega} \\
        & G(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} G_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j}) \\
        & G_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i\eta - H + E_0} S_j^{-} | \Omega \rangle
    \end{align}
\end{subequations}
where $| \Omega \rangle$ and $E_0$ are the GS and ground state energy respectively, N is the total number of spins, $\bm{R}_i$ the position of site $i$, and $\eta = 0^+$.

To extract the moment direction of a magnetic ordered phase from a cluster GS, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions. The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$
\begin{equation}
    | \Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle \label{eq:ClusterCoherentState}
\end{equation}
where the spin-1/2 coherent state
\begin{equation}
    | \theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle \label{eq:Spin-1/2CoherentState}
\end{equation}
is fully polaried along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$. By calculating the overlap between the exact cluster GS and cluster spin-conherent states, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.

@@

For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $S^x = 0$ which means that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane. An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction. When $\Gamma=0, K<0$, the moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\mathbf{S}_1$ direction. All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation. However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$.

@@

In this section, we turn to study the quantum phases in the $J-K-\Gamma$ model Hamiltonian. We consider a $4 \times 6$ cluster with PBC that has been used previously to study the KH model on triangular lattice \cite{KaiLi2015}. The resulting phase diagrams for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:PhaseDiagram}(a). The phase boundaries are obtained from the location of singular features in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$. The quantum phase diagram is closely resemble to the classical result in Ref~\onlinecite{PhysRevB.92.165108} except for the small green area near $\Gamma=1$ which does not appear in the classical phase diagram.

For pure Heisenberg model ($K=\Gamma=0$), the GS is ferromagnet for $J<0$ and 120$^\circ$ N\'{e}el state for $J>0$. As for the KH ($\Gamma=0$) mode, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified. Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(b)) and introduce the rotated spin operators $\bm{S}^{'}$: $\bm{S}_{0}^{'} = \bm{S}_0$ for sublattice 0, $\bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)$ for sublattice 1, $\bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)$ for sublattice 2, and $\bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)$ for sublattice 3. The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$. For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $\alpha^{'}=\alpha=\pi/2, tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$. When $\alpha=\pi/2, \beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$. Thus, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (dual N\'{e}el) at $\alpha=\pi/2, \beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)). The phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.

@@

When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid. To identify the remaining phases and providing more information of these phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}. For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order. Based on this observation, we propose the three blue areas with different shadings in the global phase diagram (see Fig.~\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the Sec.~\ref{sec:SectionV}. In Fig.~\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit. It is worth to note that even the GS of the classical model near the AF Kitaev point was identified to be nematic ordered which is energetically degenerate with the stripe state, our ED results favor the idea that quantum flucations would select a stripe state. The four stripe phases designated as Stripe-A, Stripe-B, Stripe-C, Stripe-D in Fig.~\ref{fig:PhaseDiagram}(a) different from each other only in the moment direction. Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:PhaseDiagram}(a). For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ and Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.

@@

\subsection{\label{sec:SectionVA}Moment direction of the FM phases}
For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction). However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction. To extract the moment direction of the FM-A and FM-C phases, we calculate the probabilities $P(\theta, \phi)$ with varying $\theta$s and $\phi$s. The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b). For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate. The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(b)).
